---
title: "Getting to Know Data Science"
author: "Calista Harris"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

## Reflections on Data Scientists vs. Statisticians

### Being a Data Scientist

From my point of view, being a data scientist involves building models and interpreting the results. They will also need skills in engineering (infrastructure, cloud systems), analysis (visualization, storytelling), and modeling/inference (prediction, explanation) to accomplish their company's requirements.

### Similarities and Differences

-   **Both** rely on hypothesis testing and regression

-   **Both** use statistical techniques to understand data and build models from real-world problems

-   **Both** must have good communication skills to communicate their results to stakeholders

-   **Data Scientist**

    -   Mainly focus on the business problem and the result

    -   Able to work with both structured and unstructured data

    -   Able to work with large amounts of data (can be messy) in various formats

-   **Statistician**

    -   Mainly focus on modeling

    -   Usually only works with structured data

    -   Usually only works with a small amount of data that has been cleaned in text file formats

### Viewing Myself

In relation to the two areas, I see myself more aligned with the statistician role. I enjoy focusing on hypothesis testing and modeling and prefer the clarity and structure that comes with working on well-defined, cleaned datasets rather than spending most of my time wrangling large, messy data across systems. The statistician’s analytical depth appeals to me more than the broad, tool-heavy demands of a data scientist.

## Iris Dataset Analysis in R

This is an analysis of the Iris dataset, specifically on the variable Petal.Width. First, will store the density of the variable Petal.Width into an object called *y*.

```{r}
y <- density(iris$Petal.Width)
```

Then, will find the class, type, and structure of *y* using functions `str()`, `typeof()`, and `str()`.
```{r}
#class
class(y)

#type
typeof(y)

#structure
str(y)
```
 
Lastly, will plot *y*.
```{r}
#| echo: false # Hide the R code in the final document 

plot(y, main = "Density of Petal Length", xlab = "Petal Length")
```